---
title: "Bayesian linear regression"
author: "Lukasz Telezynski"
date: "`r Sys.Date()`"
output: github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#blm package

##Description
blm is a R package that can be used to fit bayesian linear models. It creates blm objects and is very similar to lm().

##Usage example
First blm package needs to be loaded into R.
```{r message=FALSE}
library(blm)
```

We need some data so we generate a dataset with 2 variables x and y.
```{r }
x <- stats::rnorm(100, 10, 1)
y<- stats::rnorm(100, x, 1)
fit<-blm(y~x,1,1)
```

Finally, we can create blm object which fits linear model to our data with one explanatory variable x and response y. We need to specify formula and precision parameters alpha and beta.
```{r }
formula <- y~x
alpha <- 1
beta <- 1
fit<-blm(formula,alpha,beta)
```

Now we can print some information about our fitted model,
```{r }
summary(fit)
```


or plot some data
```{r }
plot(fit)
```

##Installation
Since blm package is available only through github, devtools package can be used to install it.

1. Install and load devtools package (ommit installation if already installed)
    ```{r eval=FALSE}
    install.packages("devtools")
    library(devtools)
    ```

2. Install blm package using devtools
    ```{r eval=FALSE}
    install_github("lttelezynski/blm")
    ```
  
##Functions
1. **blm()**  
  Constructor creating object of class blm with a fitted model. Requires data and formula in format response~explanatory.

2. **coefficients()**  
  Given blm object as an argument, returns its coefficients.
  
3. **confint()**  
  Given blm object as an argument, returns confidence intervals of coefficients. Default level=0.95 (95% CI) is used. Any value between 0 and 1 can be used. Using parm parameter with name of specific coefficient or a vector with coefficients names, confidence intervals for only that coefficient or those coefficients can be aquired.
  
4. **deviance()**  
  Given blm object as an argument, returns sum of squared distances between observed and predicted response variables.

5. **fitted()**  
  Given blm object as an argument, returns its fitted values.

6. **plot()**  
 Given blm object as an argument, plots data and regression line for datasets with only one explanatory variable.

7. **predict()**  
  Given blm object as an argument, returns predictions of response variable. New data can be passed through ... argument.
  
8. **print()**  
  Given blm object as an argument, prints out function call and coefficients.
  
9. **residuals()**  
  Given blm object as an argument, returns residuals - differences between observed and fitted values of response variable.

10. **summary()**  
  Given blm object as an argument, returns summary about fitted model.
    * Function call
    * Residuals (Min, 1Q, Median, 3Q, Max)
    * Coefficients (Estimate with 95% confidence intervals)
    * Residual standard error
    * R² and Adjusted R²
    * F-statistic and p-value
